Coupled response of stomatal and mesophyll conductance to light enhances photosynthesis of shade leaves under sunflecks

### 2016-09-22 PCE_paper/manuscript_gmes.Rmd
Amax figure edits

**Figure 2**. Photosynthetic capacity (*A*~max~) was positively correlated with mean leaf N per area (*N*~a~) for sun and shade leaves grown under elevated (ET) and ambient (AT) temperature treatments. Leaf *N*~a~ is the mean of each leaf type sampled across six gas exchange campaigns in each whole-tree chamber. *A*~max~ was measured once on all trees for each leaf type, in February 2014, at 25°C and at both saturating light and [CO~2~]. The dashed line represents the significant linear model fit for all leaves, with a marginal and conditional *R*^2^ of 0.59 and 0.62.

>>>>

**Figure 2**. Photosynthetic capacity (*A*~max~) was positively correlated with mean leaf N per area (*N*~a~) for sun and shade leaves grown under elevated (ET) and ambient (AT) temperature treatments. Leaf *N*~a~ is the mean of each leaf type, in well-watered treatments, sampled across six gas exchange campaigns in each whole-tree chamber. *A*~max~ was measured once on all trees for each leaf type, before the initiation of the drought treatment, at 25°C and at both saturating light and [CO~2~]. The dashed line represents the significant linear model fit for all leaves, with a marginal and conditional *R*^2^ of 0.59 and 0.62.
